---
title: "456 Project1 R code"
author: ""
date: "19/02/2022"
output: html_document
---

``{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(tinytex)
library(nycflights13)
library(tidyverse)
library(moderndive)
library(skimr)
library(gapminder)
library(readxl)
library(zoo)
library(gridExtra)
library(infer)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

## Data Import

```{r}
stature_hand_foot <- read_csv("C:/Users/YangTang/Desktop/456/stature_hand_foot.csv")
```


#2
```{r}
model <- lm(height ~ hand_length + foot_length, data = stature_hand_foot)

summary(model)
confint(model)
```

```{r}
ggplot(data = stature_hand_foot, mapping = aes(x = foot_length, y = height)) + geom_point() + labs(x = "FootLength(mm)", y = "Height(mm)", title = "FootLength Vs. Height") + geom_smooth(method = "lm", se = FALSE)

```

## Height with Foot

```{r}
ggplot(data = stature_hand_foot, mapping = aes(x = hand_length, y = height)) + geom_point() + labs(x = "Handlength(mm)", y = "Height(mm)", title = "HandLength Vs. Height") + geom_smooth(method = "lm", se = FALSE)
```


```{r}
a <- stature_hand_foot %>% filter(idGen < 55)
model_a <- lm(height ~ hand_length + foot_length, data = a)
summary(model_a )
confint(model_a )


b <- stature_hand_foot %>% filter(idGen >= 55)

ESS <- stature_hand_foot %>%
  mutate(ESS = ((height - (hand_length * 3.3187 + foot_length * 2.5809 + 372.5568))^2))
ESS %>%
  summarize(sum = sum(ESS))
TSS <- stature_hand_foot %>% mutate(mean_h = mean(height))
TSS <- TSS %>%
  mutate(TSS = (height - mean_h)^2)
TSS %>%
  summarize(sum = sum(TSS))


stature_hand_foot %>%
  summarize(mean = mean(height))
  
sigma(model)/mean(stature_hand_foot$height)

```